### 2018-07-19 paper/design.tex

This section presents the different parts of the system in detail.
We align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They categorize anonymous communication protocols using the following 
categories (see \cite[Table 1]{RoutingSurveyAnonymousProtocols}):
\begin{description}
  \item[Network structure]
    This describes the characteristics of the anonymous relays, the connections 
    between them and the underlying topology.
    The subcategories are
    \begin{enumerate*}
      \item network topology,
      \item connection type (direction, synchronization),
      \item symmetry (node roles, node topology for routing, decentralization).
    \end{enumerate*}

@@

Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).

Our goal is to enable private and reliable file exchange between users 
participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file $f$ 
through \name; they start by sharing some information out-of-band, \eg from 
their smartphones.
More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.

% Alice and Bob each has a set of devices containing their files, \eg a 
% smartphone, laptop and a desktop computer.
% Alice and Bob meet in a café carrying only their smartphones and Alice wants to 
% share a file, \(f\), with Bob.
% Alice's smartphone knows some metadata of \(f\) and that it resides on Alice's 
% desktop computer.
% She gives some metadata about \(f\) to Bob, at least the file size.
% Bob creates an onion route of low-availability devices with some subset of Bob's 
% devices as the destination.
% The layers of the route are chosen such that the probability of all devices 
% being offline at the same time is low.
% Bob gives this route to Alice.
% Alice's smartphone ensures that her desktop computer (containing the file \(f\)) 
% gets the route and the instruction to send \(f\) using this route.
% When Alice's desktop computer receives this instruction it will create the first 
% half of the route and concatenate it with Bob's route, then transfer \(f\) to 
% Bob.
% In this section we will present the details of the necessary algorithms.

% We have a set of users, \(U\), each user \(u\in U\) has a set of devices, 
% \(D_u\).
% We call \(D_u\) the device swarm of \(u\).
% Alice, \(a\in U\), has a device swarm, \(D_a\), and Bob, \(b\in U\) has a device 
% swarm, \(D_b\).
% We let \(D = \cup_{u\in U} D_u\) be the set of all devices, the global device 
% swarm.
% Without loss of generality, we will use Alice, with device swarm \(D_a\), and 
% Bob, with device swarm \(D_b\), as examples.

\begin{figure}[t]
\centering
\def\svgwidth{0.8\columnwidth}
%\input{outline.pdf_tex}
\import{figures/}{outline.pdf_tex}
%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
\caption{\label{fig:outline}Outline of \name's components. Users squads of devices are circled in gray. From top to bottom: a user's devices collaborate through the Squad Overlay; online devices globally share information about them to random peers; using the two above overlays allows for the creation or Predictive Onion Routes (PORs) between sets of devices; secure file exchange between users is enabled by PORs.}
\end{figure}

The privacy objectives of our system require encryption primitives that we 
first detail in \cref{BuildingBlocks}. The other constituents of \name are 
depicted in \cref{fig:outline}.
On top, the devices of each user are circled in gray, and form a user's device squad. The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior. 
This first protocol is called the \emph{Squad Overlay} and will be discussed in 
\cref{sec:squad_overlay}.
%On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}. 
Below, we see all devices connected in a random graph: each device gives 
information about itself to random nodes when it is online. This \emph{Global 
  Overlay} will be covered in \cref{sec:global_overlay}.
The information brought by these overlays allows devices to securely and 
reliably exchange messages between users by creating PORs, thus enabling file 
exchange between users, as will be explained in \cref{sec:message_passing}.
%Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.

\include*{sphinxes}
\include*{global-overlay-design}
\include*{squad-overlay-design}
%\include*{file-exchange-design}

>>>>

Our goal is to enable private and reliable file exchange between users 
participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file \(f\) 
through \name; they start by sharing some information out-of-band, \eg from 
their smartphones.
More precisely, they exchange metadata on \(f\), encryption keys, and exchange 
use-once reply mix-headers.
They use these reply headers to transfer the file contents of \(f\) over a 
network of unreliable nodes while also achieving privacy.

\begin{figure}[t]
  \centering
  \def\svgwidth{0.8\columnwidth}
  \import{figures/}{outline.pdf_tex}
  \caption{\label{fig:outline}%
    \commentDaniel{We must adapt this figure to the text.}
    Outline of \name's components. Users squads of devices are circled in gray. 
    From top to bottom: a user's devices collaborate through the Squad Overlay 
    (\cref{sec:squad_overlay}); online devices globally share information about 
    them to random peers (\cref{sec:global_overlay}); using the two above 
    overlays allows for the creation of \ac{SPOR} between sets of devices. 
    These protocols enables secure file transfer between users 
    (\cref{SPORES}).}
\end{figure}

This section presents the different parts of the system in detail.
We align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They categorize anonymous communication protocols using the following 
categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
\begin{description}
  \item[Network structure]
    This describes the characteristics of the anonymous relays, the connections 
    between them and the underlying topology.
    The subcategories are
    \begin{enumerate*}
      \item network topology,
      \item connection type (direction, synchronization),
      \item symmetry (node roles, node topology for routing, decentralization).
    \end{enumerate*}

@@

Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
This focuses on the node selection, \ie adds node selection on top of Sphinxes.
The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{} or \iac{DHT} based scheme~\cite[\eg][]{}.
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

Finally, we describe the complete \ac{SPORES} protocol (\cref{SPORES}).
\Ac{SPORES} adds an e-squad protocol to \ac{SPOR}.
This protocol provides provides each device in the e-squad of a user with 
prediction of its own and the other devices' availability.
This availability can then be used by the devices in the e-squad to participate 
as nodes for the routing of \ac{SPOR}, \ie making it \iac{P2P} system (network 
structure).

\Ac{SPORES} also allows the e-squad to act as one autonomous system, rather 
than several.
In particular, the devices will exchange information so that one device can 
receive an expected message on the behalf of another device, \eg while it is 
offline.

\include*{sphinxes}
\include*{global-overlay-design}
\include*{squad-overlay-design}
\include*{file-exchange-design}
